---
title: "Assignment 3.2"
author: "Veera Koppula"
date: "04/21/2022"
output:
  pdf_document: default
---

```{r eval=TRUE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## These two weeks we are going to be focused on line charts and step charts using various tools to create these visualizations. You must consolidate all the charts into ONE document with each chart labeled with the type of chart and technology - for example: Python - Bar Chart.  
```{r eval=TRUE, echo=FALSE}
setwd("/Users/veerareddykoppula/Downloads/Desktop/BRUIN/640_Data_Visualization/640/Assignment/Week5_6/")
# Import required packages
library('magrittr')

# Import data to be used for visualization
dir = paste(getwd(),'ex3-3',sep = '/')
file_expenditures = 'expenditures.txt'
file_unemployement = 'unemployement-rate-1948-2010.csv'

raw_expenditures =  read.table(paste(dir,file_expenditures,sep='/'), header = TRUE, sep = '\t', dec = '.', fill = TRUE)

raw_unemployement = read.csv2(paste(dir,file_unemployement,sep='/'), sep=',', stringsAsFactors = FALSE) %>% 
    dplyr::mutate(Value = as.numeric(Value)) %>% 
    as.data.frame()

# Examine data
print(head(raw_expenditures))
print(head(raw_unemployement))

```

### Tree Map
#### Mapping how much each category has costed
```{r eval=TRUE, echo=FALSE}
treemap::treemap(raw_expenditures,index = c('category'),
                 vSize = 'expenditure',
                 title = 'Expenditure by Category', 
                 palette = 'RdYlGn')
```

### Area Chart
#### Mapping average value over the years, from the unemployment dataset
```{r eval=TRUE, echo=FALSE}
avg_unemployement = raw_unemployement %>%
    dplyr::group_by(Year) %>%
    dplyr::summarize('Average Value' = mean(Value))

head(avg_unemployement)

ggplot2::ggplot(avg_unemployement, ggplot2::aes(x=Year , y=`Average Value`)) +
ggplot2::geom_area( fill='blue', alpha=.2) +
ggplot2::geom_line() +
ggplot2::ggtitle('Average Value by Year')
```
### Stacked Area Chart
#### Mapping the trend of the expenditure of each category over the years.
```{r eval=TRUE, echo=FALSE}
ggplot2::ggplot(raw_expenditures, ggplot2::aes(x=year, y=expenditure, fill=category)) + 
  ggplot2::geom_area()
```
